### 2020-03-01 ChapterConclusion/chapterConclusion.tex
Updated: Conclusion extension, bullet points for contributions and small fixes

\chapter{Conclusions and Future Work}
\section{Conclusions}
An approach to networked real-time physics simulations that is scalable and alleviates the processing limitation of a single server has been presented. Only open-source software has been used in our approach and our algorithm has been developed in a way that is agnostic to any specific application technology.

In Chapter \ref{ProbDef} the challenges facing distributed real-time physics were defined, possible solutions were addressed and our chosen solution, AP, was presented and justified. The origination of the aura calculation used for the auras in AP was also presented. The implementation of AP was discussed in Chapter \ref{Implementation}, including potential topologies that could be used by a system using AP and the breakdown of the components of each server. Chapter \ref{Implementation} also gave an overview of the visualiser used by the system, which is responsible for rendering the state of the simulation through the use of replicas. Its features and their implementation details were discussed.

In Chapter \ref{Results}, the design and results of the experiments were presented for addressing the questions set out by this study: "Can scalable real-time physics simulations be achieved?" and "Can real-time physics simulations remain correct when scaled?".

The experiments carried out in this study establish that the approach is scalable, as demonstrated by the addition of servers improving the performance of the system when simulating an increasingly large number of objects. This study has demonstrated that a standard real-time physics engine (in this case, PhysX) may be incorporated into our scalable real-time physics system and achieve performance that is acceptable for real-time distributed simulations such as networked games.

The correctness of collisions in AP have been measured and evaluated. The experiments conducted in this study establish that collisions remain correct in AP, even when objects interact while intersecting the boundary. This has been shown to be true while increasing each of the following factors: speed; latency and frame-time. Collisions remain correct up to the tolerance values for each factor and begin to show errors as soon as the tolerance is exceeded, demonstrating the correctness of the aura calculation used in AP. The holds true if thrashing collisions are excluded from the results. The number of thrashing collisions and amount of times thrashed were both measured, potential solutions to the thrashing problem were proposed in \ref{Thrashing} and we assume that these errors will be fixed in future work.

>>>>

\chapter{Conclusions and Future Work}
\section{Conclusions}
An approach to networked real-time physics simulations that is scalable and alleviates the processing limitation of a single server has been presented. Only open-source software has been used in this study's approach and the algorithms used in AP have been developed in a way that is agnostic to any specific application technology.

In Chapter \ref{ProbDef} the challenges facing distributed real-time physics were defined, specifically why maintaining consistency is necessary in real-time physics and the difficulties of maintaining consistency when latency is present. Possible solutions were addressed and this study's proposed solution, AP, was presented and justified. AP provides eventual consistency for the states of objects through the use of auras and strong consistency for collisions between objects, by ensuring any two objects that are possibly colliding are simulated on the same server. The origination of the aura calculation used for the auras in AP was also presented. The implementation of AP was discussed in Chapter \ref{Implementation}, including potential topologies that could be used by a system using AP and the breakdown of the components of each server. Chapter \ref{Implementation} also gave an overview of the visualiser used by the system, which is responsible for rendering the state of the simulation through the use of replicas. Its features and their implementation details were discussed.

In Chapter \ref{Results}, the design and results of the experiments were presented for addressing the questions set out by this study: 
\begin{itemize}
	\item "Can scalable real-time physics simulations be achieved?"
	\item "Can real-time physics simulations remain correct when scaled?"
\end{itemize}

The experiments carried out in this study establish that the approach is scalable, as demonstrated by the addition of servers improving the performance of the system when simulating an increasingly large number of objects. This study has demonstrated that a standard real-time physics engine (in this case, PhysX) may be incorporated into this study's scalable real-time physics system and achieve performance that is acceptable for real-time distributed simulations such as networked games.

The correctness of collisions in AP have been measured and evaluated. The experiments conducted in this study establish that collisions remain correct in AP, even when objects interact while intersecting the boundary. This has been shown to be true while increasing each of the following factors: speed; latency and frame-time. Collisions remain correct up to the tolerance values for each factor and begin to show errors as soon as the tolerance is exceeded, demonstrating the correctness of the aura calculation used in AP. The holds true if thrashing collisions are excluded from the results. The number of thrashing collisions and amount of times thrashed were both measured, potential solutions to the thrashing problem were proposed in \ref{Thrashing} and it can be assumed that these errors will be fixed in future work.
